Paper_stuff

### 2023-11-12 Paper_stuff.Rmd
Domographic variables coding

## Rename and Recode variables 
We can change the current variables to make them easier to interpret. 
#recode varaibles
Mothership <- mutate(Mothership, 
                     DC_status_1 = as.factor(DC_status_1),
                     DC_status_1 = recode(DC_status_1,
                                          "1"="Complete",
                                          "2"="Nearly Complete",
                                          "3"="Insurance",
                                          "4"="Nonatteneance",
                                          "5"="Inappropriate",
                                          "6"="Inpatient",
                                          "7"="Withdrew",
                                          "8"="Dissatisfaction",
                                          "9"="Other"),
                     Education_1 = as.factor(Education_1),
                     Education_1 = recode(Education_1,
                                          "1"="<Grade 12",
                                          "2"="HS Diploma",
                                          "3"="GED",
                                          "4"="Some College",
                                          "5"="Associates Degree",
                                          "6"="Bachelors Degree",
                                          "7"="Some Grad School",
                                          "8"="Grad Degree"),
                     Gender_1 = as.factor(Gender_1),
                     Gender_1 = recode(Gender_1,
                                       "0"="Female",
                                       "1"="Male",
                                       "2"="Non-Binary",
                                       "3"="Other",
                                       "4"="Unknown"),
                     Relationship_1 = as.factor(Relationship_1),
                     Relationship_1 = recode(Relationship_1,
                                             "0"="Married",
                                             "1"="Cohabitating",
                                             "2"="Widowed",
                                             "3"="Separated",
                                             "4"="Divorced",
                                             "5"="Never Married"),
                     Sexuality_1 = as.factor(Sexuality_1),
                     Sexuality_1 = recode(Sexuality_1,
                                          "1"="Straight",
                                          "2"="Gay",
                                          "3"="Bisexual",
                                          "4"="Other"),
                     IPT_track_1 = as.factor(IPT_track_1),
                     IPT_track_1 = recode(IPT_track_1,
                                          "0"="General",
                                          "1"="Trauma",
                                          "2"="Young Adult",
                                          "3"="BPD"),
                     Race_1 = as.factor(Race_1),
                     Race_1 = recode(Race_1,
                                     "0"="White",
                                     "1"="Black",
                                     "2"="Hispanic",
                                     "3"="Asian",
                                     "4"="Portugese",
                                     "5"="Other"),
                     Education_1 = as.factor(Education_1),
                     Education_1 = recode(Education_1,
                                      "0"="<Grade 6", 
                                      "1"="Grades 7-12",
                                      "2"="HS Diploma", 
                                      "3"="GED",
                                      "4"="Some College",
                                      "5"="Associates Degree",
                                      "6"="Bachelors Degree",
                                      "7"="Some Grad School",
                                      "8"="Grad Degree"),
                     DC_status_1 = as.factor(DC_status_1),
                     DC_status_1 = recode(DC_status_1,
                                      "1"="Treatment Complete",
                                      "2"="Treatment Near Complete",
                                      "3"="Insurance Stopped",
                                      "4"="Nonattendence",
                                      "5"="Inapproparite Language",
                                      "6"="Transfered To Impatient",
                                      "7"="Withdrew for External factors",
                                      "8"="Withdrew (AMA)",
                                      "9"="Other",
                                      "10"="Other"),
                    DC_status_1 = as.factor(DC_status_1),
                    DC_status_1 = recode(DC_status_1,
                                      "1" ="Inpatient",
                                      "2" ="PHP",
                                      "3" ="APS",
                                      "4" ="Psychatrist",
                                      "5" ="PCP",
                                      "6" ="Another Physican",
                                      "7" ="Therapist",
                                      "17"="Other",
                                      "11"="Other",
                                      "0" ="Other"
                    ),

@@

#Extract Year From Intake Date
#Convert to Date
library("lubridate")
Mothership$Intake_1<-ymd(Mothership$Intake_1)
Mothership$TxYear<-as.numeric(format(Mothership$Intake_1,"%Y"))
Mothership<-mutate(Mothership,
                   TxYear = as.factor(TxYear),
                   TxYear = recode(TxYear,
                                   "1582"="2014"))
```

@@

#Demographic tab
Demo_tab<-data.frame(table1::table1(~Age_1+Education_1+Race_1+Gender_1+Relationship_1, data=Demo_tab_df))
colnames(Demo_tab) <- c("Variable","Total Sample")
Demo_tab

@@

#### DEP
ggplot(data=DEP_PrePost_mean,
       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
           group=Disorder_Type,color=Disorder_Type))+
  geom_point(size=2.5)+
  geom_line(size=1)+
  scale_x_discrete(name="Time Point")+
  scale_y_continuous(name="CUDOS Score")+
  labs(title = "Mean Pre and Post Depression Scores By Disorder Type",
       subtitle = "Self report depression was assessed using the CUDOS",
       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title = element_blank())

@@

AnxDep_Treat_mean<-AnxDep_PrePost_Long %>%
  filter(!is.na(Sig_unresponse),
         !is.na(Disorder_Type)) |>
  group_by(Test,Disorder_Type,Sig_unresponse,PrePost) %>%
  summarise(Score=mean(Score,na.rm=TRUE))

p <- ggplot(data=AnxDep_Treat_mean,
       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
           group=Test,color=fct_rev(Test)))+
  geom_point(size=2.5) +
  geom_line(group=AnxDep_Treat_mean$PrePost,size=1.5)+
  scale_x_discrete(name="Time Point")+
  scale_y_continuous(name="CUDOS/CUXOS Score")+
  labs(
    title = "Mean Pre and Post Scores of the Anxiety and Depression",
    subtitle = "Treatment response based upon Disorder")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title = element_blank()) +
  facet_grid(Sig_unresponse~Disorder_Type,
             labeller = labeller(
               Sig_unresponse = c("1" = "Non-responders", "2" = "Responders"),
               Disorder_Type = c("1" = "Anxiety", "2" = "BPD", "3" = "Mood", "4" ="Other", "5" = "Trauma")
      ))
p 
#Anxiety     BPD    Mood   Other  Trauma
```

@@

```{r}
Mothership_Long_anx <- gather(Mothership,rm,CUXOS,Day1_CUXOS:Day40_CUXOS,factor_key = "T")
Mothership_Long_anx <- Mothership_Long_anx[order(Mothership_Long_anx$ID1),]

@@

@@

>>>>

## Rename and Recode variables 
We can change the current variables to make them easier to interpret. 
```{r}
#recode varaibles
Mothership <- mutate(Mothership, 
                     Education_1 = as.factor(Education_1),
                     Education_1 = recode(Education_1,
                          "1"="<Grade 12",
                          "2"="HS Diploma or GED",
                          "3"="HS Diploma or GED",
                          "4"="Some College/Associates Degree",
                          "5"="Some College/Associates Degree",
                          "6"="Bachelors Degree",
                          "7"="Bachelors Degree",
                          "8"="Grad Degree"),
                     Gender_1 = as.factor(Gender_1),
                     Gender_1 = recode(Gender_1,
                          "0"="Female",
                          "1"="Male",
                          "2"="Non-Binary",
                          "3"="Other",
                          "4"="Other"),
                     Relationship_1 = as.factor(Relationship_1),
                     Relationship_1 = recode(Relationship_1,
                          "0"="Married or Cohabitating",
                          "1"="Married or Cohabitating",
                          "2"="Widowed or Seperated",
                          "3"="Widowed or Separated",
                          "4"="Divorced",
                          "5"="Single or Never Married"),
                     Sexuality_1 = as.factor(Sexuality_1),
                     Sexuality_1 = recode(Sexuality_1,
                          "1"="Straight",
                          "2"="Gay",
                          "3"="Bisexual",
                          "4"="Other"),
                     IPT_track_1 = as.factor(IPT_track_1),
                     IPT_track_1 = recode(IPT_track_1,
                          "0"="General",
                          "1"="Trauma",
                          "2"="Young Adult",
                          "3"="BPD"),
                     Race_1 = as.factor(Race_1),
                     Race_1 = recode(Race_1,
                                     "0"="White",
                                     "1"="Black",
                                     "2"="Hispanic",
                                     "3"="Asian",
                                     "4"="Portugese",
                                     "5"="Other"),
                    DC_status_1 = as.factor(DC_status_1),
                    DC_status_1 = recode(DC_status_1,
                                      "1" ="Inpatient",
                                      "2" ="PHP",
                                      "3" ="APS",
                                      "4" ="Psychatrist",
                                      "5" ="PCP",
                                      "6" ="Another Physican",
                                      "7" ="Therapist",
                                      "8"="Withdrew (AMA)",
                                      "9"="Other",
                                      "10"="Other",
                                      "11"="Other",
                                      "17"="Other",
                                      "0" ="Other"),

@@

#Extract Year From Intake Date
#Convert to Date
library("lubridate")
Mothership$Intake_1<-ymd(Mothership$Intake_1)
Mothership$TxYear<-as.numeric(format(Mothership$Intake_1,"%Y"))
Mothership<-mutate(Mothership,
                   TxYear = as.factor(TxYear),
                   TxYear = recode(TxYear,
                                   "1582"="2014"))

str(Mothership$Education_1)
```

@@

#Demographic tab
Demo_tab<-data.frame(table1::table1(~Age_1+Race_1+Education_1+Gender_1+Relationship_1, data=Demo_tab_df))
colnames(Demo_tab) <- c("Demographic","Total Sample")
Demo_tab

@@

#### DEP
ggplot(data=DEP_PrePost_mean,
       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
           group=as.factor(Disorder_Type),color=as.factor(Disorder_Type)))+
  geom_point(size=2.5)+
  geom_line(size=1)+
  scale_x_discrete(name="Time Point")+
  scale_y_continuous(name="CUDOS Score")+
  labs(title = "Mean Pre and Post Depression Scores By Disorder Type",
       subtitle = "Self report depression was assessed using the CUDOS",
       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title = element_blank())

@@

AnxDep_Treat_mean<-AnxDep_PrePost_Long %>%
  filter(!is.na(RESPONDER_FIGS),
         !is.na(Disorder_Type)) |>
  group_by(Test,Disorder_Type,RESPONDER_FIGS,PrePost) %>%
  summarise(Score=mean(Score,na.rm=TRUE))

p <- ggplot(data=AnxDep_Treat_mean,
       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
           group=Test,color=fct_rev(Test)))+
  geom_point(size=2.5) +
  geom_line(group=AnxDep_Treat_mean$PrePost,size=1.5)+
  scale_x_discrete(name="Time Point")+
  scale_y_continuous(name="CUDOS/CUXOS Score")+
  labs(
    title = "Mean Pre and Post Scores of the Anxiety and Depression",
    subtitle = "Treatment response based upon Disorder")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title = element_blank()) +
  facet_grid(RESPONDER_FIGS~Disorder_Type,
             labeller = labeller(
               RESPONDER_FIGS = c("1" = "Non-responders", "2" = "Responders"),
               Disorder_Type = c("1" = "Anxiety", "2" = "BPD", "3" = "Mood", "4" ="Other", "5" = "Trauma")
      ))
p 
#Anxiety     BPD    Mood   Other  Trauma
```

@@

```{r}
Mothership_Long_anx <- gather(Mothership_post,rm,CUXOS,Day1_CUXOS:Day40_CUXOS,factor_key = "T")
Mothership_Long_anx <- Mothership_Long_anx[order(Mothership_Long_anx$ID1),]

@@

Mothership_Mean_CUXOS2 <- Mothership_Long_anx %>%
  group_by(Duration,RESPONDER_FIGS,TxDay) %>%
  summarise(Score=mean(CUXOS,na.rm=TRUE))

View(Mothership_Mean_CUXOS2)

@@

length of treatment based upon response?
```{r}

bg_col <- "#F9FBF2"
# highlight_col <- "#FFAD05"
# highlight_col <- "FF52825"
highlight_col <- "#02d46e"
outline_col <- "darkblue"
dark_col <- "#333333"

str(Mothership_post$Days_complete_1)
subset(Mothership, !is.na(Gender_1))
ggplot(
  data = subset(Mothership_post, !is.na(RESPONDER_FIGS)),
  mapping = aes(
    x = Days_complete_1,
    y = Disorder_treat,
    group = Disorder_treat)
  )+
  geom_jitter(
    size = 0.6,
    alpha = .5,
   colour = highlight_col
    )+
  geom_boxplot(
    outlier.shape = NA,
   colour = outline_col,
   fill = highlight_col,
    alpha = 0.3) +
  scale_x_continuous(
   breaks = c(0, 15, 30, 45, 60),
    limits = c(0.00, 60)
  ) +
  facet_wrap(~RESPONDER_FIGS)

      #        labeller = labeller(RESPONDER_FIGS =
      # c("1" = "Non-Responders", 
      #   "2" = "Responders"))

summary(Mothership_post$Days_complete_1)

table1(Days_complete_1, data = Mothership_post)
#####W WHY ARE DAYS COMPLETE NOT SHOWING UP???
